Abstractions for Multi-Sorted Substitutions

### 2023-09-19 paper/paper.tex
Update.

  Benton et al.\cite{DBLP:journals/jar/BentonHKM12} addresses this
  issue by duplicating the definitions and using tactics to reduce
  boilerplate in proofs.
  In contrast, we define structures similar to \ACode{\ACon{Kit}} and
  \ACode{\ACon{Traversal}}, which allow us to abstract over all four
  compositions and use the same trick as before to eliminate the
  dependencies.
  This has the benefit, that we can prove lemmas about
  the composition of arbitrary maps, which enable us later to unify type
  preservation of all substitution and renaming operations into a single
  lemma.
  % TODO: clarify

@@

  To fill this gap, we introduce a new abstraction that we call a
  \ACode{\ACon{ComposeKit}},
  which provides an operation \ACode{\AField{\_\&/⋯\_}} that unifies
  \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}. This allows us to
  define a general composition in the spirit of:
  \ExampleCode\KComposition
  We then define a \ACode{\ACon{ComposeTraversal}}, which consists of the
  \ACode{\AField{⋯-fusion}} lemma for general maps.

  Just like a \ACode{\ACon{Traversal}} allowed us to bootstrap the two
  \ACode{\ACon{Kit}} instances, the \ACode{\ACon{ComposeTraversal}} allows
  us to bootstrap the four \ACode{\ACon{ComposeKit}} instances.

@@

  Using the \ACode{\ACon{WkKit}}, we then define
  the \ACode{\ACon{ComposeKit}} and \ACode{\ACon{ComposeTraversal}}
  structures, which serve analogous purposes to \ACode{\ACon{Kit}}
  and \ACode{\ACon{Traversal}} from before:
  the library provides a \ACode{\ACon{ComposeKit}} for each of the
  four compositions, whereas the \ACode{\ACon{ComposeTraversal}}
  structure needs to be instantiated by the application with
  lemmas parameterized over arbitrary \ACode{\ACon{ComposeKit}}s.
  This gives the user a composition operation
  \ACode{\AField{\_·ₖ\_}} between arbitrary maps and corresponding
  lemmas, instead of multiple definitions and lemmas about concrete
  maps, enabling us to reason on a more abstract level and to avoid
  further boilerplate.

@@

  \AppCode\FFusion
  \AppCode\FFusionProofInteresting
  The interesting cases are:
  \begin{itemize}
  \item 
  \end{itemize}

>>>>

  Previous work on kits\cite{DBLP:journals/jar/BentonHKM12} addresses this
  issue by duplicating the definitions and using tactics to reduce
  boilerplate in proofs.
  In contrast, we define structures similar to \ACode{\ACon{Kit}} and
  \ACode{\ACon{Traversal}}, which allow us to abstract over all four
  compositions and use the same trick as before to eliminate the
  dependencies.
  This has the benefit, that we can prove lemmas about
  the composition of arbitrary maps, which enable us later to unify type
  preservation of all substitution and renaming operations into a single
  lemma.
  % TODO: clarify

@@

  To fill this gap, we introduce a new abstraction that we call a
  \ACode{\ACon{ComposeKit}},
  which provides an operation \ACode{\AField{\_\&/⋯\_}} that unifies
  \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}. This allows us to
  define a general composition, which informally can be described as:
  \ExampleCode\KComposition
  We then define a \ACode{\ACon{ComposeTraversal}}, which consists of the
  \ACode{\AField{⋯-fusion}} lemma for general maps.
  Just like a \ACode{\ACon{Traversal}} allowed us to bootstrap the two
  \ACode{\ACon{Kit}} instances, the \ACode{\ACon{ComposeTraversal}} allows
  us to bootstrap the four \ACode{\ACon{ComposeKit}} instances.

@@

@@

  \AppCode\FFusion
  \AppCode\FFusionProofInteresting
  The interesting cases are:
  \begin{itemize}
  \item
    variables, where we need to use the \ACode{\AField{\&/⋯-⋯}} lemma
    provided by the \ACode{\ACon{ComposeKit}}.
  \item
    bindings, where the traversal operation \ACode{\AField{\_⋯\_}}
    needs to lift the map via \ACode{\AField{\_↑\_}}, requiring us to
    distribute the lifting over the composition using
    \ACode{\AField{dist-↑-·}}.
  \end{itemize}
